---
title: "Sai Srikar Bandaru_M3_Project"

output: html_document
---
---
title: "SAI SRIKAR BANDARU_M3_PROJECT"
output: html_document
---

<html>
<head></head>
<body>

<CENTER>
<FONT SIZE=4, COLOR="Black"><B>M3_PROJECT_Assignment_1</B>
<P>
Your name: SAI Srikar Bandaru
<BR>
Your class name: ALY6000 
<BR>
Your instructor's name: Dr. Dee Chiluiza, PhD
<BR>
Date of submission: 02/04/2022
</FONT>
</CENTER>
<P>

---

<P><BR>
<FONT SIZE=3, COLOR="#8272E9">
<B>INTRODUCTION</B>
<FONT SIZE=3, COLOR = "#000000">

1.<BR>
-> Descriptive analysis - they are simply break down of basic statistical numbers which are presented in s raw form to taking a colorful picture. And also they are quite different to Inferential Statistics. Some of metrics, we encounter are measures of despertion, central deviation and distribution of data from quantiles. Further we can also decipher if curve is normal or skewed.  <BR>
-> 
    <BR>https://www.academia.edu/60366759/Assessing_Statistical_Reasoning_in_Descriptive_Statistics_A_Qualitative_Meta_Analysis accessed on 02/04/2022
    
    <BR>https://www.researchgate.net/post/For_a_paper_that_is_not_a_review_can_it_contain_only_descriptive_statistical_analysis  accessed on 02/01/2022
    

2.<BR>

Technology byitself is not resource and its here we need to domain knowledge which can be levereged to take business decisions. Coming to Fishing industry, its no different, highly important to respect the laws and principles of indsutry which was estb decades ago. Definetly, Tech and automation will act as a catalyst for better results without compromising the resources. 
 

<BR>https://www.sciencedirect.com/science/article/pii/S0308597X20308988?via%3Dihub

<BR>https://www.mdpi.com/2071-1050/13/11/6037 accessed on 02/03/2022

3.<BR>
R has gained popularity from late 90s for this interface and sound statistical modelling. In addition,the in built functions and coding is very user friendly making it a popular tool for hands-on projects undertakings. 
<BR>Optimization - Policy making and Management.
<BR>Netflix/Application - Recommendation systems .
<BR>Sports - Create real time reports and build strategies.
<BR>E-commerce & Retail - Obtain results based on people preferences and bias. 
<BR>
</FONT>

---
<P>
---

<P><BR>
<FONT SIZE=3, COLOR="#8272E9">
<B>ANALYSIS SECTION</B>
<BR></FONT>
<P>

---
Library Data
---

```{r}
# loading the necessary libraries!!!
library(readr)

library(readxl)

library(openxlsx) #To read csv and xlsx type dataset types

library(tidyverse)

library(dplyr)

library(plyr)

library(magrittr)

library(FSAdata)

library(base)

library(fishdata)

library(knitr)

library(kableExtra)

library(DT) # Inorder tp create interactive tables

library(FSA)
library(RColorBrewer)

xyxyz = read_excel("C:/MPS NEU/ALY6000/Data sets/inchBioM.xlsx")

```


<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
<BR>
</FONT></B>

<P>

```{r}
summary(xyxyz)
```

<B><FONT SIZE=3, COLOR="#000000">
<BR>Summary is a function that outputs the statistical values columnwise for the numerical dataset 
<BR>And for the categorical values summary gives out the central tendency and counts of the different variables 
<BR>
</FONT></B>


<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
2nd TASK
</FONT></B>

<P>

```{r}
tibble::glimpse(xyxyz)
```

<BR>the function glimpse in tibble gives row wise dataset as a somma seperated set here with number of rows and columns in the given table 
<BR>
</FONT></B>



<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
3rd TASK
</FONT></B>

<P>

```{r}
#nrow(xyxyz)
#ncol(xyxyz)
NCOL(xyxyz)
NROW(xyxyz)
mean(xyxyz$length)
mean(xyxyz$weight)

# Answers to the questions in this task are neatly presentled below.
print(paste("number of variables: ", ncol(xyxyz)))
print(paste("number of observations: ", nrow(xyxyz)))
print(paste("Mean of length is", round(mean(xyxyz$length), 2)))
print(paste("mean of weight: ", round(mean(xyxyz$weight),2)))

```

<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
Task 4
</FONT></B>

<P>

```{r}
library(tidyverse)
knitr::kable(FSA::headtail(select(xyxyz,c(3:5)),6), caption = "First, Last 6")
#datatable can also used for the same task.


```


<P>
<B><FONT SIZE=3, COLOR="#982855">
5th TASK
</FONT></B>

<P>

```{r}

bio = as.data.frame(table(xyxyz$species))
colnames(bio)=c("Species","Frequency")
datatable(bio)
freq = bio$Frequency
Spe = bio$Species
bio=mutate(bio,CF=cumsum(freq))
CF = bio$CF
bio=mutate(bio,Per=round(freq/sum(freq)*100,2))
bio=mutate(bio,CP=cumsum(bio$Per))

knitr::kable(bio, caption = "Updated table")

```

<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
6th TASK
</FONT></B>

<P>

```{r Task 6, message=FALSE, warning=FALSE}
par(mai=c(1.1,2.2,1,1))

b1=barplot(freq~Spe,horiz = T,las=1,xlim=c(0,270),
             cex.axis=0.6,col=terrain.colors(6),
             main = "Species and Frequency",xlab = "Frequency",ylab = "")
text(freq,b1,freq,pos = 3)

b2=barplot(CF~Spe,horizontal = T,las=2,xlim=c(0,320),
             cex.axis=0.8,col=terrain.colors(9),
             main = "Cumulative Frequency v/s Species",xlab = "Cumulative Frequency",ylab = "")
text(CF,b1,CF,pos = 4)

b3=barplot(bio$Per~Spe,horizontal = T,las=1,xlim=c(0,70),
             cex.axis=0.7,col=terrain.colors(7),
             main = "Box Plot_Percent",xlab = "Percentage",ylab = "")
text(bio$Per,b1,bio$Per,pos = 3.5)

b4=barplot(bio$CP~Spe,horiz = T,las=1,xlim=c(0,110),
             cex.names = 0.4,
           col=brewer.pal(7,"PuOr"),
             main = "Cumulative Percent",xlab = "Cumulative Percentage",ylab = "")
text(bio$CP,b1,bio$CP,pos = 4)

```

<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
7th TASK
</FONT></B>
  
<P>

```{r Task 7, message=FALSE, warning=FALSE}


par(mai=c(1, 2,1.1,1))

t7=barplot(freq~Spe,horizontal = T,
               las=1,xlim=c(0,250),cex.axis=0.8,
               col=brewer.pal(7,"PiYG"),main = "Sai Srikar Bandaru",xlab = "",ylab = "",cex.names=0.4)
title(xlab="Frequency", line=2.5, cex.lab=1.8, col.lab="#330066")
 title(ylab="Species", line=6, cex.lab=1.2, col.lab= "Blue")
text(freq,b1,Spe,pos = )

```

<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
8th TASK Cumulative_%.
</FONT></B>
  
<P>


```{r Task 8, message=FALSE, warning=FALSE}
par(mai=c(1.3,1.6,1,2.5))

t8_plot = barplot(xyxyz$freq, width=0.7, space=1,borders=NA, ylim=c(0,700), cex.names=0.7, names.arg=Spe, main = "Sai Srikar Bandaru", las=1,col= colorRampPalette(2,1))
  axis(side = 2,at=c(0,220),las=1,col.axis="green",col = "blue",cex.axis=0.8)
  axis(side = 4, at= c(0,CF), las =1, col.axis = "green",
        col = "Red", cex.axis = 0.8)
   mtext("Frequency", side=2, line=3, cex.lab=1, las=1, col="red")
   mtext("Cumulative Frequencies", side=4, line=2, cex.lab=2, las=1, col="red")
   lines(t8_plot, CF, type = "b", cex = 0.6, pch = 1.9, col="Blue") 

```

<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
9th TASK 
</FONT></B>

<P>

```{r Task 9, message=FALSE, warning=FALSE}

box <- boxplot(xyxyz$length ~ xyxyz $species,
        main="Length ~ Species",
        xlab="Species",
        ylab="Length column",
        ylim=c(0,600),
        las=1,
        col=c("Violet"),
        frame.plot=FALSE,
        boxwex=0.6,
        outline = TRUE,
        staplewex = 0.9,
        cex.name = 0.4,
        cex.lab = 1.2)

```

<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
10th TASK 
</FONT></B>

<P>

```{r , message=FALSE, warning=FALSE}
plot <- (xyxyz %>% 
           filter(species %in% c("Iowa Darter","Bluntnose Minnow")))

box_df <- boxplot((plot$length ~ plot$species),
las = 1,
main = "Bluntnose Minnow ~ Iowa Darter",
boxwex = 0.5,
xlab = "Species",
ylab = "Length",
cex.name = 0.7,
cex.lab = 2,
col = "#982855",
outline = TRUE)
text(y=boxplot.stats(plot$length)$stats,
    labels = round(boxplot.stats(plot$length)$stats,0),
x = 1.5,
cex = 0.5,
col ="Maroon")

```



<P><BR>
<B><FONT SIZE=3, COLOR="#982855">
Task 11. Scatter plot
</FONT></B>

<P>

```{r Task 11, message=FALSE, warning=FALSE}

plot(xyxyz$length,xyxyz$weight,
     col=c("Red","yellow"),
     xlab = "Length",
     ylab = "Weight",
     pch=c(3,20))

```

<P>
---
Final sections
---

<!--Title for Conclusions section-->
<P><BR>
<FONT SIZE = 4, COLOR = "#8272E9"><B>
CONCLUSIONS
</B></FONT>

<P>


<!--Title for Bibliography section-->
<P><BR>
<FONT SIZE = 3, COLOR = "#8272E9"><B>
BIBLIOGRAPHY
</B></FONT>


<B><FONT SIZE=3, COLOR="#000000">
<BR> With assignments becoming more prominent in the last few weeks, I have taken strides to learn tricks of the trade coming to report making and presentation skills.
<BR>https://www.sportscidata.com/how-to-create-interactive-reports-with-r-markdown-part-i/ as accessed on 01/29/2022
<BR>  https://www.mathworks.com/help/stats/boxplot.html accessed on 1/24/2022
<BR> For several questions, I have used references from Prof. Dee, Phd  <BR> 
<BR> https://discdown.org/rprogramming/reporting.html 
<BR>
</FONT></B>

<P>


<!--Title for Appendix section-->
<P><BR>
<FONT SIZE = 3, COLOR = "#8272E9"><B>
APPENDIX
</B></FONT>


<B><FONT SIZE=3, COLOR="#000000">
<BR>
</FONT></B>

<P>



</body>
</html>